Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
last pages

\TODO{Beware, there are incoherences between the automaton and the
  rules, e.g. OT3 goes to state 01, or 01 ?}

@@

\TODO{Discussion: next steps: 1) what is left as open questions on the
  algorithm itself, what you have learned (is Z3 useful and efficient,
  is it the right tool ?). 2) next important goal is bisimulation
  checking, what is neded for that (formalize the algo, define and
  implement simplification)}

Among the questions arides during this work, an important one is the
efficiency of Z3 for our needs. Z3 is famous for being very fast for
solving very large sets of assertions, and this could be important for
us. But we encountered  some problems during the implementation the
checking method using Z3. For example, if the $functions$ and the
$datatypes$ part of the algebra presentation we submit to the solver
are independent with each other, then checking the $assertions$ is a
simple work. However, $functions$ on recursive $datatypes$ make it
more complex, some special rules might be defined by user for the
induction. Also, we need more evidence that dealing with more complex
action algebras, that would involve axiomatizing their dat structures
into Z3 theories, will indeed allow us to decide validity of
predicates.
We may also try other automatic theorem provers, depending on th
estructure of the proofs we need.

>>>>

@@

Among the questions arising during this work, an important one is the
efficiency of Z3 for our needs. Z3 is famous for being very fast for
solving very large sets of assertions, and this could be important for
us. But we encountered  some problems during the implementation the
checking method using Z3. For example, if the $functions$ and the
$datatypes$ part of the algebra presentation we submit to the solver
are independent with each other, then checking the $assertions$ is a
simple work. However, $functions$ on recursive $datatypes$ make it
more complex, some special rules might be defined by user for the
induction. Also, we need more evidence that dealing with more complex
action algebras, that would involve axiomatizing their dat structures
into Z3 theories, will indeed allow us to decide validity of
predicates.
We may also try other automatic theorem provers, depending on th
estructure of the proofs we need.
